Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-28 paper/ijcai16.tex
paper: modificato conclusioni

A PC configurations is defined by eight attributes: computer type (laptop,
desktop, or tower), manufacturer (8 choices), CPU model (37), monitor size (8), RAM amount (10), storage (10)
size, and price.
%See Table~\ref{tab:pcdataset} for an overivew of the attributes.
The price attribute is defined as a linear combination of the other
attributes: this is a fair modeling choice, as often the price of a PC is
well approximated by sum of the price of its components plus an offset due to
branding.
%
Interactions between attributes are expressed as Horn clauses. An example
constraint might look like this: ``if the manufacturer is Apple, then the
CPU must be either a PowerPC G3 or a PowerPC G4''\footnote{Despite the components
included in the dataset, which are a bit outdated, the dataset itself is pretty
realistic.}, which can be encoded
into MILP form as
%
$ (1 - x_\text{Apple}) + x_\text{G3} + x_\text{G4} \ge 1 $.
%
Note that mutual exclusivity between all binary variables of the
one-hot encoding of an attribute ensures that only one of
$x_\text{G3}$ and $x_\text{G4}$ can be 1.  The dataset includes
constraints between the following attributes: manufacturer $\to$ type,
manufacturer $\to$ CPU, type $\to$ RAM amount, type $\to$ storage
size, type $\to$ monitor size, for 16 Horn constraints total. We do
not report the full list due to space limitations. Note that the
search space is of the order of hundreds of thousands of candidate
configurations, and is far beyond reach of existing Bayesian
approaches. Furthermore, existing Bayesian preference elicitation
approaches are designed for categorical attributes and cannot deal
with (even dependent) continuous features like the price. \andrea{@andrea: mention Bonilla}

@@

We presented a max-margin approach for generating a set of diverse
examples.  Our approach, that can be seen as an extension of maxmargin
learning to sets, is effective in the generation of a diverse set of
items that can be used to ask informative queries to the user.  The
main advantages of our elicitation method are 1) its aptitude for
eliciting preferences and providing recommendations in large
configuration problems 2) robustness with respect to erroneous
preference input, and 3) its ability to encourage sparse utility
functions.  In a number of experiments we showed how our method
compare with state-of-the-art approaches.

@@

% \begin{figure}[b]
%     \centering
%     {\footnotesize
%     \begin{tabular}{cccc}
%         \hline
%         \multicolumn{2}{c}{{\sc loss/time per iter.}} &
%         \multicolumn{2}{c}{{\sc loss/time per query}}
%         \\
%         \multicolumn{4}{c}{{\sc sparse uniform}}
%         \\
%         \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
%         \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
%         \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
%         \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}
%         \\
%         \hline
%         \multicolumn{4}{c}{{\sc sparse normal}}
%         \\
%         \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_loss} &
%         \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_time} &
%         \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_loss} &
%         \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_time}
%         \\
%         \hline
%     \end{tabular}
%     }
%     \caption{\label{fig:pc} Results for {\sc SetMargin} on the constructive PC
%     dataset.}
% \end{figure}

\twocolumn

>>>>

A PC configurations is defined by eight attributes: computer type (laptop,
desktop, or tower), manufacturer (8 choices), CPU model (37), monitor size (8), RAM amount (10), storage (10)
size, and price.
%See Table~\ref{tab:pcdataset} for an overivew of the attributes.
The price attribute is defined as a linear combination of the other
attributes: this is a fair modeling choice, as often the price of a PC is
well approximated by sum of the price of its components plus an offset due to
branding.
%
Interactions between attributes are expressed as Horn clauses. An example
constraint might look like this: ``if the manufacturer is Apple, then the
CPU must be either a PowerPC G3 or a PowerPC G4''\footnote{Despite the components
included in the dataset, which are a bit outdated, the dataset itself is pretty
realistic.}, which can be encoded
into MILP form as
%
$ (1 - x_\text{Apple}) + x_\text{G3} + x_\text{G4} \ge 1 $.
%
Note that mutual exclusivity between all binary variables of the
one-hot encoding of an attribute ensures that only one of
$x_\text{G3}$ and $x_\text{G4}$ can be 1.  The dataset includes
constraints between the following attributes: manufacturer $\to$ type,
manufacturer $\to$ CPU, type $\to$ RAM amount, type $\to$ storage
size, type $\to$ monitor size, for 16 Horn constraints total. We do
not report the full list due to space limitations. Note that the
search space is of the order of hundreds of thousands of candidate
configurations, and is far beyond reach of existing Bayesian
approaches.

@@

We presented a max-margin approach for efficient preference
elicitation in large configuration spaces. Our approach relies on an
extension of max-margin learning to sets of hyperplanes, and is
effective in the generation of a diverse set of items that can be used
to ask informative queries to the user.  The main advantages of our
elicitation method are 1) its ability to elicit preferences and
provide recommendations in large configuration problems 2) its
robustness with respect to erroneous feedback and 3) its ability to
encourage sparse utility functions. Experimental comparisons against
state-of-the-art Bayesian preference elicitation strategies confirm
its substantial computational advantages. For sparse utility
functions, the method compares favourably also in terms of the number
of queries asked to the user.

@@

\begin{figure*}
    \centering
    {\footnotesize
    \begin{tabular}{cccc}
        \hline
        \multicolumn{2}{c}{{\sc loss/time per iter.}} &
        \multicolumn{2}{c}{{\sc loss/time per query}}
        \\
        \multicolumn{4}{c}{{\sc sparse uniform}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_uniform_sparse_per_query_time}
        \\
        \hline
        \multicolumn{4}{c}{{\sc sparse normal}}
        \\
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_iter_time} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_loss} &
        \includegraphics[width=10em]{figures/pc_with_costs_normal_sparse_per_query_time}
        \\
        \hline
    \end{tabular}
    }
    \caption{\label{fig:pc} Results for {\sc SetMargin} on the constructive PC
    dataset.}
\end{figure*}
